---
title: "Crime Rates in Toronto"
author: 
  - Meha Grewal
thanks: "Code and data are available at: https://github.com/meha-g/Paper1."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Neighbourhood crime rates in the city of Toronto is essential data to understand illegal activity in the city. We cleaned and analyzed crime statistics in 2020 based on different crimes using graphs.. Third sentence (our findings). Fourth sentence (why it matters)."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(janitor)
library(opendatatoronto)
library(lubridate)
library(tidyverse)
library(tidyr)
```

# Introduction

First paragraph is going to be motivational and broad.

Second paragraph about what was done and what was found 

Third paragraph about implications 

Remainder of this paper is: Section \@ref(data) explains the data. Section \@ref(results) covers results... 


### Data

Paragraph or two introducing data set broadly.
Our data is of ...


```{r bills, fig.cap="Bills of penguins", echo = FALSE}
#ggplot(penguins, aes(x = island, fill = species)) +
 # geom_bar(alpha = 0.8) +
  #scale_fill_manual(values = c("darkorange","purple","cyan4"),
   #                 guide = FALSE) +
  #theme_minimal() +
  #facet_wrap(~species, ncol = 1) +
  #coord_flip()

```

## Data Download
#From Open Data Toronto https://open.toronto.ca/dataset/neighbourhood-crime-rates/

```{r}
# get package
package <- show_package("fc4d95a6-591f-411f-af17-327e6c5d03c7")
package

# get all resources for this package
resources <- list_package_resources("fc4d95a6-591f-411f-af17-327e6c5d03c7")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the first datastore resource as a sample
data <- filter(datastore_resources, row_number()==1) %>% get_resource()
data

crime_dat <- read.csv("/Users/meha/Documents/YEAR 3/STA304/neighbourhood-crime-rates.csv")
```

Show an extract of the data (Table \@ref(tab:dataextract))
```{r dataextract}
crime_dat %>% 
  select(Neighbourhood, AutoTheft_2020, Assault_2020, Robbery_2020)
  slice(1:10) %>%  
  kable(
    caption = "First ten rows of a dataset of economic indicators for 
    Australia, Ethiopia, India, and the US",
    col.names = c("Neighbourhood", "Auto Theft", "Assualt", "Robbery"),
    digits = 1
  )
```




## Cleaning the Data 

```{r}

```




```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References

