---
title: "Crime Rates in Toronto"
author: 
  - Meha Grewal
thanks: "Code and data are available at: https://github.com/meha-g/Paper1."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Neighbourhood crime rates in the city of Toronto is essential data to understand illegal activity in the city. We cleaned and analyzed crime statistics in 2020 based on different crimes using graphs.. Third sentence (our findings). Fourth sentence (why it matters)."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(janitor)
library(opendatatoronto)
library(lubridate)
library(tidyverse)
library(tidyr)
```

# Introduction

First paragraph is going to be motivational and broad.

Second paragraph about what was done and what was found 

Third paragraph about implications 

Remainder of this paper is: Section \@ref(data) explains the data. Section \@ref(results) covers results... 


### Data

Paragraph or two introducing data set broadly.
Our data is of ...

We obtained our data set using the 'opendatatoronto' package from the City of Toronto's Open Data Portal [@citeopendatatoronto] and the statistical programming language R [@citeR]

## Data Download
From Open Data Toronto https://open.toronto.ca/dataset/neighbourhood-crime-rates/

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# get package
#package <- show_package("fc4d95a6-591f-411f-af17-327e6c5d03c7")
#package

# get all resources for this package
#resources <- list_package_resources("fc4d95a6-591f-411f-af17-327e6c5d03c7")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
#datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the first datastore resource as a sample
#data <- filter(datastore_resources, row_number()==1) %>% get_resource()
#data

crime_dat <- read.csv("/Users/meha/Documents/YEAR 3/STA304/neighbourhood-crime-rates.csv")
```

Show an extract of the data (Table \@ref(tab:dataextract))
```{r dataextract, echo=FALSE, warning=FALSE, message=FALSE}
crime_dat %>% 
  select(Neighbourhood, AutoTheft_2020, Assault_2020, Robbery_2020) %>% 
  slice(1:10) %>%  
  kable(
    caption = "First ten rows of a dataset of crime rates for auto thefts, assault, and robbery.",
    col.names = c("Neighbourhood", "Auto Theft", "Assualt", "Robbery"),
    digits = 1,
    booktabs = TRUE,
    linesep =""
  )
```

Paragraph or two more about Table (Table \@ref(tab:dataextract))

## Cleaning the Data 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Checking for missing variables in data set
dat <- is.na(crime_dat)


```

Our data set is of crime rates (Figure \@ref(fig:rates))

We are interested in the number of homicides from the years 2014 to 2020 since this showcases the current trends of dangerous crimes being committed and its implications for the safety of neighborhoods in Toronto.  

Figure (Figure \@ref(fig:rates)) displays the pattern of homicides in Toronto between the years of 2014-2020
```{r rates, fig.cap="Homicide rates in Toronto", echo=FALSE, warning=FALSE, message=FALSE}

```

Talk way more about it. 


## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References

